Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-13 paper-1/manuscript.tex
Fixed missing test indicator

To show that $\D{}{}$ captures not only changes in $V_m$, by definition, but also in the resulting response, we correlated $\Delta \D{A}{i}$ with $\Delta \R{A}{i}$ across neurons of the sample network. Notice that this mirrors the correlation shown in Figure \ref{fig4} between $\Delta \T{A}{i}$ and $\Delta \R{A}{i}$. As shown in Figure \ref{fig8}b, the relationship was clearly negative (Pearson's $\rho$ = -0.541, p = 2.28e-77; Wald test, n = 1000), indicating that higher $\D{}{}$ causes reduced responses as expected. We confirmed this relationship across networks and stimuli, see Figure \ref{fig8}c, and found that greater depression in \dev{} predicted a lower response in most networks (T = 724, p = 1.37e-14), though the median correlation coefficient $\rho$ was only -0.282. We note that calculating this same correlation in the model with STD only yields no significantly negative dependence (T = 3.99e+03, p = 0.828; see Figure \ref{sfig8}).

>>>>

To show that $\D{}{}$ captures not only changes in $V_m$, by definition, but also in the resulting response, we correlated $\Delta \D{A}{i}$ with $\Delta \R{A}{i}$ across neurons of the sample network. Notice that this mirrors the correlation shown in Figure \ref{fig4} between $\Delta \T{A}{i}$ and $\Delta \R{A}{i}$. As shown in Figure \ref{fig8}b, the relationship was clearly negative (Pearson's $\rho$ = -0.541, p = 2.28e-77; Wald test, n = 1000), indicating that higher $\D{}{}$ causes reduced responses as expected. We confirmed this relationship across networks and stimuli, see Figure \ref{fig8}c, and found that greater depression in \dev{} predicted a lower response in most networks (T = 724, p = 1.37e-14; one-sided Wilcoxon, n = 120), though the median correlation coefficient $\rho$ was only -0.282. We note that calculating this same correlation in the model with STD only yields no significantly negative dependence (T = 3.99e+03, p = 0.828; see Figure \ref{sfig8}).
